\section{Amnesiac Diviner of the Sea}
Some say that every great man's story begins at their birth. Others prefer starting the story at an important event that set them on the path they would go on. If we were to go with the latter school of thought, we'd say that your story truly begins during a sea battle. You were essentially a sailor with Cassandra's curse - blessed with the ability to see the future, cursed with the fate of not being believed by anyone. \textit{"It's a trap!"} you said, but the captain didn't listen to you. Your ship was ambushed, your ship was captured, your crew was massacred, and you were thrown into the sea to feed the sharks - yet, somhehow, you lived, washed ashore a nameless island. Whether it was because you hit your head extra hard some time along the line, or because of traumatic experience, you now have amnesia, barely remember anything about the past before the battle. How tragic to be able to tell others' future, but not your own past, isn't it?\newline
\textbf{Bonuses:}
\begin{itemize}
	\item Basic Seamanship for free
	\item Your character has premotions of sorts, and can tell if something is wrong in an \textit{"I have a bad feeling about this"} way. The GM has to take this into account, albeit not to the point of metagaming. The character can also vaguely tell the fate of others via some form of diviniation.
\end{itemize}
\textbf{Maluses:}
\begin{itemize}
	\item You can only choose 14 feats at the beginning, instead of the usual 16.
	\item Low amount of starting money.
\end{itemize}
