\section{Orphaned Paladin}
Most valiant holy knights are of aristocratic blood - but you are not. Truth is, you have no idea who your ancestors were - either they died very early, or they consciously threw you into the trash can as an infant, only for you to be found by wandering knights, who took you in. Through either fate or just luck, once you grew to the apropriate age, they started treating you like a future apprentice, and thus, your life path was set for you from the start. Having trained from a very early age, you are good with weapons and holy magic alike, but the hard years of training didn't really let you explore other areas, thus your skills suffer in just about everything else.\newline
\textbf{Bonuses:}
\begin{itemize}
	\item Medium Armour Conditioning for free.
	\item Basic Flurry for free.
	\item Basic Overswing for free.
	\item Basic Riding for free.
	\item Advanced Horsemanship for free.
	\item Basic Chevauchée for free.
	\item Advanced Swords for free.
	\item Advanced Literacy \Parentheses{at your native language} for free.
	\item Basic knowledge of the Classical High Elven language \Parentheses{Classical Language feat} for free.
	\item Basic Etiquette for free.
	\item Magica Divinitatis for free.
	\item Basic Photomancy for free.
\end{itemize}
\textbf{Maluses:}
\begin{itemize}
	\item You can only pick 4 feats at the start, instead of the usual 16.
	\item You are forbidden from taking on Bows, Crossbows or Firearms as your starting feats. If you stray from the path of the Paladin, you can acquire them later on though.
	\item As long as your character remains a dutiful Paladin, he cannot take on the Bows, Crossbows, Firearms, Sciomancy and Necromancy feats. This is a soft rule meant to be enforced by the GM, as long as the character doesn't go through a significant alignment shift \Parentheses{that is, straying away from Lawful Good}.
	\item Mediocre amount of starting money.
\end{itemize}
