\subsection{Foreign Language}
The language skill is special in that it is not a single feat, but rather a group of feats that covers a character's fluency in a language.


\textbf{Requirements:}
\begin{itemize}
	\item \textbf{Basic:} The language in question not being the character's native tongue.
	\item \textbf{Advanced:} None.
	\item \textbf{Expert:} None.
\end{itemize}
\textbf{Effects:}
\begin{itemize}
	\item \textbf{Untrained:} The character cannot speak that language, and cannot understand anything from it, unless their own native language is closely related to \textit{(and preferably mutually intelligible with)} the language in question.
	\item \textbf{Basic:} The character has some level of fluency at the language in question, but makes a lot of errors in grammar and pronounciation alike, has a very noticeable accent and a limited vocabulary. Overall, the character knows enough to get them in and out of trouble, but not much else.
	\item \textbf{Advanced:} The character is fluent at the language. While still having an accent, and the occasional grammatical hiccup, they can both understand and speak the language confidently.
	\item \textbf{Expert:} The character is as fluent at the language as a native speaker - if not more. They not only speak it with perfect grammar and pronounciation, but can also utilize it to a degree that would make even some poets green with envy. Unless the character has intentionally made it their trademark, the character no longer has an accent.
\end{itemize}\newpage
