\subsection{Profession}
The Profession skill is special in that it is not a single feat, but rather a group of feats that covers a character's skill at a mundane profession that are typically pursued by normal people who aren't adventurers - some of these might still come useful to adventurers on special occasions though, like when an obelisk asks an adventurer a question only an Expert Shoemaker could answer. Some professions may also allow the character to craft certain items.


\textbf{Requirements:}
\begin{itemize}
	\item \textbf{Basic:} Nothing.
	\item \textbf{Advanced:} Nothing.
	\item \textbf{Expert:} Nothing.
\end{itemize}
\textbf{Effects:}
\begin{itemize}
	\item \textbf{Untrained:} The character has no experience in or any real knowledge about that profession. Even if someone attempts to teach it to them, they will inevitably forget it in a day.
	\item \textbf{Basic:} The character knows the basics of the trade in question, and could make a fine assisstant to an actual master, but nothing more.
	\item \textbf{Advanced:} The character knows far more than what can be expected from an assistant, but not enough to make them a master of their trade. If the character was to retire from their life of adventure, they could make a decent living out of pursuing that profession, but would be unable to fufill the desires of more refined customers.
	\item \textbf{Expert:} The character is an expert of the trade in question, and if they were to encoutner an oracle or genie who makes a riddle only solvable by someone with considerable knowledge in that field, they could solve it. Their skill effectively gives them a safety net, a Plan B if the whole adventuring business turns out to be less lucrative than initially expected, as they know the profession enough to make a good living out of it.
\end{itemize}\newpage
%\section{Mundane Professions}
%\subsection{Smithing}
%\subsection{Weaponsmithing}
%\subsection{Armoursmithing}
%\subsection{Wheelcrafting}
%\subsection{Woodworking}
%\subsection{Carpentry}
%\subsection{Shoemaking}
%\subsection{Needlework}
%\subsection{Herbalism}
%\subsection{Farming}
%\subsection{Hunting}
%\subsection{Cooking}
