\chapter{Playable Primary Races}
 \input{races/01-playable/Humans.tex}
 \input{races/01-playable/HighElves.tex}
 \input{races/01-playable/WoodElves.tex}
 \input{races/01-playable/DarkElves.tex}
 \input{races/01-playable/HalfElves.tex}
 \input{races/01-playable/HalfOrcs.tex}
 \input{races/01-playable/Orcs.tex}
 \input{races/01-playable/Ogres.tex}
 \input{races/01-playable/Goblins.tex}
 \input{races/01-playable/Halflings.tex}
 \input{races/01-playable/Gnomes.tex}
 \input{races/01-playable/Dwarves.tex}
 \input{races/01-playable/Lizardmen.tex}
 \chapter{Non-Playable Primary Races}
 \textbf{Non-PLayable races} are races that, while not explicitly forbidden, are not recommended for usage as player characters for various reasons. They will not be playable in any of the video game adaptations either, and they are not recommended for tabletop usage either, other than as NPCs controlled by the game master. The reasons for this vary a lot, but boil down to these so-called \SoCalled{non-playable races} being...
 \begin{itemize}
 	\item ...unballanced, thus giving players who control them an unfair \Parentheses{dis}advantage.
 	\item ...not as fleshed out as the so-called so-called \SoCalled{playable races}
 	\item ...not fitting into the traditional formula of characters having attributes, classes and equipment. As a rule of thumb, non-bipedal races are automatically non-playable in the Occident.
 \end{itemize}
 As previously stated, while playing as characters from these races is not explicitly forbidden per se, it is genuinely not recommended for game masters to let players create characters from these races. These races will also be non-playable in any future video game adaptations.
 \input{races/02-non-playable/Nereids.tex}
 \input{races/02-non-playable/Angels.tex}
 \input{races/02-non-playable/Dragons.tex}
 \input{races/02-non-playable/Griffins.tex}
 \input{races/02-non-playable/WingedCobras.tex}
 \chapter{Secondary Races}
 \textbf{Secondary races} are races that people aren't usually born into, but instead are turned into, usually via some sort of magic. Most secondary races are undead, and their condition is caused by a symbiotic relationship between their own animated corpse and a tiny creature that is responsible for the animation: the only cure to such a condition is a final death.
 \input{races/03-secondary/Liches.tex}
 \input{races/03-secondary/Vampires.tex}
 \input{races/03-secondary/Theriantropes.tex}
