\section{Adventuring Mobster}
You're no ordinary citizen - you're a shanty-zen, someone who hails from the slums of a big city. Not only that, but you were also part of a mob, a gang or a mafia. You were - and still are - a criminal, though not necessary a petty thief, burglar or saltbird: maybe you were all of those or neither, but what is certain is that you were a footsoldier for a mafia, and this gave you certain privileges. 

But now that is in the past. Either you went too far and killed someone you shouldn't have, were caught red-handed at embezzling some of the profits, stole something, killed a fellow mobster or did something else that pissed off the boss - whatever the case, you were branded an anathema, and targeted for being killed as swiftly as possible, forcing you out of the slums. So where'dja go? The Inner City might be a safe place for someone wanting to escape the mob, but you lacked the money to permanently settle down there, and you saw most honest work as beneath you. So you did the logical thing: you skipped town.

A fish out of the urban water, now you're an adventurer walking the countryside, looking for mercenary work - or maybe a chance to redeem yourself as part of a heroic group of adventurers.

\textbf{Bonuses:}
\begin{itemize}
	\item You start with the Advanced Street Smarts, Basic Bludgeoners and Basic Crossbows feats for free.
	\item You can choose an Advanced Weapon feat for free - or two Basic ones instead. Alternatively, if you choose Advanced Bludgeoners or Advanced Crossbows, you can choose a Basic one for free.
\end{itemize}


\textbf{Maluses:}
\begin{itemize}
	\item You may only pick 12 feats at the beginning instead of the usual 16.
	\item You cannot choose Etiquette or Logic as your starting feats. You can still acquire them later on though.
	\item You might get a nasty surprise waiting for you, if you return to the slums of your home town. \Parentheses{Up to the GM to enforce}
	\item Very low starting money.
\end{itemize}
