\section{Crook}
\SoCalled{\href{https://www.youtube.com/watch?v=OCsMKypvmB0}{Stop right there, criminal scum!}} - a sentence you heard all too often in your life. You're a crook. There is no better way to describe you, unless you consider the words \SoCalled{criminal}, \SoCalled{thief} or \SoCalled{burglar} to be more flattering. Whether you chose the criminal life or it chose you, your experiences made you a hardenned \Parentheses{wo}man - you've been in jail \Parentheses{\href{https://tvtropes.org/pmwiki/pmwiki.php/Main/HadToComeToPrisonToBeACrook}{you have to go to jail to be a crook after all}}, you narrowly escaped with your life several times before, and hey, you know the saying: what doesn't kill you, makes you stronger, right? Well, it may not have made you physically stronger, it definitely made you a decent thief. Effectively, you have become a career criminal.

However, not being content with petty theft in the slums, you have grown ambitious and made up your mind: you are going to look for greener pastures as a wandering crim- err, adventurer with the intention of honing your thieving skills and stealing some great relic in order to get rich quick. Who knows, maybe a group of desperate adventures might recruit you out of need for your skills.

\textbf{Bonuses:}
\begin{itemize}
	\item You start with the Basic Street Smarts feat, Basic Pickpocket, Basic Sneaking and Basic Lockpicking feats
	\item Mediocre starting money.
\end{itemize}


\textbf{Maluses:}
\begin{itemize}
	\item You cannot choose Etiquette or Naturalism as your starting feats. You can still acquire them later on though.
	\item You are a wanted criminal in your home territory. \textit{(enforcement up to the GM)}
\end{itemize}
