\section{Failed Surgeon}
\SoCalled{The path to hell is paved with good intentions} - or so goes the saying. You weren't always an evil villain filled with a lust for power - once you were a goodly surgeon with one fatal flaw: you always came too late to save their lives, so, out of desperation, you decided to research into forbidden fields.

This came with two drawbacks: the first and most obvious one was that this forbidden knowledge marked you as an outcast, got you kicked out of whatever institution your worked for, and made you a wanted criminal despite having done no real crimes. The second, less obvious one was the fact that this dark power you have acquired ended up twisting your mind. The once good doctor became an evil necromancer full of lust for power. Or maybe your mind was already fickle and did not need any supernatural power to twist it: your persecution at the hands of the \SoCalled{champions of the light} made you question all their dogmas about selflessness, and you accidentally fell off the other side of the horse. Either way, now your main motivation is your own growth.

\textbf{Bonuses:}
\begin{itemize}
	\item Magica Profana, Basic Surgery, Basic Sciomancy and Necromancy for free
	\item Advanced Literacy with your native language's script
	\item Basic Literacy with the Despotanmagi script and basic knowledge of Despotanmagi \Parentheses{Basic Classical Language feat}
\end{itemize}


\textbf{Maluses:}
\begin{itemize}
	\item You can only pick 10 feats at the start, instead of the usual 16.
	\item Low amount of starting money.
\end{itemize}
