\section{Thrillseeking Bard}
True glory consists in doing what deserves to be written, in writing what deserves to be read - and you wish to attain glory in both fields.

You're a bard. A man or woman who walks the earth with a lute in their hand and songs on their lip. Every hero worth their salt has a hundred poems and songs written in their praises - and after reciting so many poems and singing so many songs in praises of heroes of old, something snapped in your brains, and decided that you want to be just like those heroes of the old. You will save the world, \textbf{AND} leave behind the catchiest tunes of all!

As a bard, you start with good music skills - otherwise you wouldn't have survived as a bard - and some money saved from all the donations of people who liked your songs. You also carry a sword in addition to your lute, combined with a good deal of self-righteous indignation and a burning desire to spread honour and justice in the world - or just to go from tavern to tavern to brag about your heroic deeds \Parentheses{real and fictional alike} in order to get laid, or succesfully beg for enough coin to buy enough booze to get wasted.

For better or worse, you think you're the hero the world needs and deserves.

\textbf{Bonuses:}
\begin{itemize}
	\item You start with the following feats for free: Advanced Music, Advanced Diaesthese, Basic Swords, Basic Sneaking
	\item You receive a Steel Shortsword and a Wooden Lute as bonus starting items.
\end{itemize}
\textbf{Maluses:}
\begin{itemize}
	\item You get to choose only 12 feats at the start instead of 16
	\item Low amount of starting money.
\end{itemize}
