\section{Vampire Hunter}
Hunting vampires is not a unique profession - paladins, inquisitors, errant brothers, even some city guards do it from time to time. However, those people either do it out of a \Parentheses{sense of} religious duty, or because they're told - you're different. For you, it's personal.

Perhaps one of those bloodsucking fiends killed your father, or brother, your wife or your best friend. Perhaps you saw an innocent girl gored to death by a frenzied undead abomination, and could barely escape with your life. Whatever the case, you took it upon yourself to train for your own personal crusade against the creatures of the night. At your disposal is a diverse set of tools to fight against these horrible creatures - but with great power comes great danger, and this especially applies to vampire hunters like you: the more vampires you kill, the more your reputation grows, the more unwanted attention you will receive from those you aren't powerful enough to take on. And woe be to you, if they manage to bite your neck instead of killing you, for vampires love turning vampire hunters into vampires.\newline
\textbf{Bonuses:}
\begin{itemize}
	\item Free choice between Magica Profana, Magica Divinitatis or Magica Naturae for free
	\item Basic Pyromancy
	\item Basic Enchantment
	\item Basic Sneaking
	\item Basic Crossbows
	\item Basic Exotic Weapons
	\item Advanced Literacy with your native language's script
\end{itemize}
\textbf{Maluses:}
\begin{itemize}
	\item You can only pick 10 feats at the start, instead of the usual 16.
	\item Low amount of starting money.
	\item Extra unwanted attention from vampires trying to turn you. \Parentheses{Up to GM to enforce}
\end{itemize}
