\section{Asinine Assassin}
Let's face it - you're not particularly good looking. No, you're actually quite ugly: you have the face of a donkey! Not only the face, but you also have the temperament of a donkey. You're stubborn, once you set your mind on anything - literally anything - you will not rest until you get it done, no matter how many times you fail. Just one problem with that: you're an assassin! Your job is supposed to be sneaking into safe spaces, silently assassinating your targets, while preferably leaving no witnessess, and leaving just as silently as you came.

Having a face that only a mother could love may help you blend into more unrefined masses and pretend to be the hunchback of some famous cathedral, it certainly won't help you when you try to pretend to be a prince here to see a noble whose death is wanted by some creditors. Still, because you constantly to either fight off or outrun those who tried to violently bully you for your unsavoury looks, you have developed extra strength and dexterity - both useful in the assassination business. Your affinity with equines is also noteworthy.


\textbf{Bonuses:}
\begin{itemize}
	\item \Bonus{1} on Strength and Dexterity
	\item Free feats: Advanced Sneaking, Basic Lockpicking, Basic Riding, Advanced Horsemanship, Basic Exotic Weapons, Basic Crossbows
\end{itemize}


\textbf{Maluses:}
\begin{itemize}
	\item \Malus{2} on charisma
	\item You get to choose only 10 feats at the start instead of 16
	\item Low amount of starting money.
\end{itemize}
