\section{Dragon's Blood}
Under normal circumstances, dragons cannot interbreed with the various humanoid races of this world, be they mammalian \Parentheses{humans, elves, orcs, goblins, ogres, halflings, dwarves, gomes} or reptilian \Parentheses{lizardmen} - however, this is a world of magic, where \SoCalled{normal circumstances} don't exist, and even the seemingly impossible is possible.

Ever since you were born \Parentheses{or hatched from the egg, if you're a lizardman}, your dream was to fly, you had the eyes of a snake, your blood had a rather odd smell and colour, and you were convinced that your mother's husband - if you even had one in the first place - is not your biological father \Parentheses{or maybe you have similar suspicions about your paternal grandfather instead?}. When you look at the sky, an unexplainable feeling of longing overcomes you; when you are angry, there are literal flames in your eyes; you do not hold the gods \Parentheses{or God, if the religion you were brought up in is monotheistic} in particularly high regard, and you see the divine laws as unnecessary chains on you.

It is beyond any doubt, that the blood of a dragon courses through your veins, and even the most knowledgeable of sages would struggle to explain how you came to be - that didn't stop you from becoming an adventurer possibly motivated by finding out the truth about your heritage and origins.

\textbf{Bonuses:}
\begin{itemize}
	\item Resistance the element of Fire.
	\item Resistance to offensive Arcane Magic directed at you.
\end{itemize}

\textbf{Maluses:}
\begin{itemize}
	\item \Malus{4} to Charisma.
	\item You cannot cannot acquire \textbf{Magica Divinitatis} \Parentheses{Clerical Magic}. If you want to play as a spellcaster, your only choices are \textbf{Magica Profana} \Parentheses{Arcane Magic} or \textbf{Magica Naturae} \Parentheses{Nature Magic}.
	\item Low starting money.
\end{itemize}
