\section{Wandering Monk}
Not all monks spend their time in their monasteries hugging books and praying all day long - some monks wander the lands and walk the earth, for various reasons: to spread their faith and proselytize, to collect ancient artifacts in their church's name \Parentheses{so that their head of religion can hoard them}, or to just act out their religion's commandements in the wild: which, for Light-aligned monks, would mean being a good samaritan, healing the sick, helping those in need and hunting down the demons and the undead - and for Dark-aligned monks, it would be spreading pain and suffering, one can presume. 


\textbf{Bonuses:}
\begin{itemize}
	\item The following feats for free: Advanced Martial Arts, Basic Logic, Advanced Literacy \Parentheses{at your native language}, Basic Etiquette, Magica Divinitatis.
	\item Light-aligned Monks start with Advanced Photomancy. Dark-aligned Monks start with Advanced Sciomancy. Neutral-aligned Monks either start with bonus magic feats defined by their religion, or alternatively, if undefined, start with Basic Geomancy and Basic Aeromancy.
	\item Light-aligned Monks - Monks of Titanius - start with Advanced knowledge of the Classical High Elven language \Parentheses{Classical Language feat}. Other monks instead start with Expert Literacy at their native language's script, instead of Advanced.
\end{itemize}


\textbf{Maluses:}
\begin{itemize}
	\item You can only pick 6 feats at the start, instead of the usual 16.
	\item Light-aligned Monks are forbidden from starting with - and later taking on - any weapon or armour feats, save for Polearms.
	\item Light-aligned Monks can never learn Sciomancy as long as they remain on the path of light - likewise, Dark-aligned monks can never learn Photomancy as long as they remain on the Path of Dark. For other monks, this is defined for their religion.
	\item The character can never learn Necromancy - not even Dark-aligned Monks, as every religion in existence \Parentheses{even Dark-aligned ones} abhors the practice and agree that desecrating the dead is a serious sin that should not be tolerated.
	\item Low amount of starting money.
\end{itemize}
